---
title: "Codebook"
author: "Dave"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}

## Make sure the appropriate packages are installed
## 

require(dplyr)
require(data.table)

knitr::opts_chunk$set(echo = FALSE)
```

## Course 3 Final Project Codebook  

The function run_analysis() produces a tidy dataset in the file 
"tidy_dataset.csv".  That file contains the following variables: 

### Order and grouping variables

The dataset is grouped and ordered by Subject, then Activity.  The activity variable is a factor - it's ordering is specified by Levels.  

Variable|Class|Description
---|---|-----------
Subject|Num|The number of the participant.  Each participant will have 6 entries, One for each activity  
Activity|Factor|The actvities that were identified through accelerometer data. Levels = WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING  

***
### Mean of Motion Data Variables  

The assignment called for the mean of a subset of the provided data.  Only measurements of  

- mean  
- std  

are to be part of the output.  All variables are numeric.  Their names are as follows:  


```{r show_varnames}

knitr::opts_chunk$set(fig.width=12)

tidy_set <- fread("https://raw.githubusercontent.com/yachabach/R-Project---Course-3-Final/master/tidy_dataset.csv")

colnames(tidy_set[,3:length(colnames(tidy_set))])
```
***
```{r show_sample}

knitr::opts_chunk$set(fig.width=12)

tidy_set[1:20,1:5]
```

