---
title: "Codebook"
author: "Dave Yachabach"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}

## Make sure the appropriate packages are installed
## 

require(dplyr)
require(data.table)

knitr::opts_chunk$set(echo = FALSE)
```

## Course 3 Final Project Codebook  

The function run_analysis() produces a tidy dataset in the file 
"tidy_dataset.csv".  That file contains the following variables: 

### Order and grouping variables

The dataset is grouped and ordered by Subject, then Activity.  The activity variable is a factor - it's ordering is specified by Levels.  

Index|Variable|Class|Description
--|---|---|-----------
1|Subject|Num|Participant's identifying number.  Each participant will have 6 entries, one for each activity  
2|Activity|Factor|The actvities that were identified through accelerometer data. Levels = WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING  

***  
### Mean of Motion Data Variables  

The assignment called for a tidy dataset of the mean of certain variables.  Only variables with measurements of  

- mean  
- std  

are to be part of the output.  All variables are numeric.  Their indexes and names in the "tidy_dataset.csv" file are as follows:  


```{r show_varnames}

tidy_set <- fread("https://raw.githubusercontent.com/yachabach/R-Project---Course-3-Final/master/tidy_dataset.csv")

name_set <- data.table("Variable Index" = 1:length(tidy_set), "Variable Name" = colnames(tidy_set))

knitr::kable(name_set, align = 'cl')
```

***  

### Small Sample of tidy_dataset structure  
This is an example of the structure of tidy_dataset.  It is ordered by Subject and then by activity.  Since Activity is a factor, it is ordered by the file Activity_Labels.txt in the original data.  This sample only displays the means of first 4 of 86 mean motion variables.  

```{r show_sample}

knitr::kable(tidy_set[1:20, 1:6], align = 'clcccc')
```

