---
title: "Codebook"
author: "Dave"
date: "8/14/2020"
output: html_document
---

```{r setup, include=FALSE}

## Make sure the appropriate packages are installed
## 

require(data.table)
require(dplyr)

knitr::opts_chunk$set(echo = FALSE)
```

## Course 3 Final Project Codebook  

The function run_analysis() produces a tidy dataset in the file 
"tidy_dataset.csv".  That file contains the following variables: 

### Order and grouping variables

The dataset is grouped and ordered by Subject, then Activity.  The activity variable is a factor - it's ordering is specified by Levels.  

Variable|Class|Description
---|---|-----------
Subject|Num|The number of the participant.  Each participant will have 6 entries, One for each activity  
Activity|Factor|The actvities that were identified through accelerometer data. Levels = WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING  

### Mean of Motion Data Variables  

The assignment called for the mean of only the 86 variables containing "mean" or "std" from the 561 variables available in the original dataset.  All variables are numeric.  Their names are as follows:

[1] "tBodyAcc-mean()-X"                    "tBodyAcc-mean()-Y"                   
 [3] "tBodyAcc-mean()-Z"                    "tBodyAcc-std()-X"                    
 [5] "tBodyAcc-std()-Y"                     "tBodyAcc-std()-Z"                    
 [7] "tGravityAcc-mean()-X"                 "tGravityAcc-mean()-Y"                
 [9] "tGravityAcc-mean()-Z"                 "tGravityAcc-std()-X"                 
[11] "tGravityAcc-std()-Y"                  "tGravityAcc-std()-Z"                 
[13] "tBodyAccJerk-mean()-X"                "tBodyAccJerk-mean()-Y"               
[15] "tBodyAccJerk-mean()-Z"                "tBodyAccJerk-std()-X"                
[17] "tBodyAccJerk-std()-Y"                 "tBodyAccJerk-std()-Z"                
[19] "tBodyGyro-mean()-X"                   "tBodyGyro-mean()-Y"                  
[21] "tBodyGyro-mean()-Z"                   "tBodyGyro-std()-X"                   
[23] "tBodyGyro-std()-Y"                    "tBodyGyro-std()-Z"                   
[25] "tBodyGyroJerk-mean()-X"               "tBodyGyroJerk-mean()-Y"              
[27] "tBodyGyroJerk-mean()-Z"               "tBodyGyroJerk-std()-X"               
[29] "tBodyGyroJerk-std()-Y"                "tBodyGyroJerk-std()-Z"               
[31] "tBodyAccMag-mean()"                   "tBodyAccMag-std()"                   
[33] "tGravityAccMag-mean()"                "tGravityAccMag-std()"                
[35] "tBodyAccJerkMag-mean()"               "tBodyAccJerkMag-std()"               
[37] "tBodyGyroMag-mean()"                  "tBodyGyroMag-std()"                  
[39] "tBodyGyroJerkMag-mean()"              "tBodyGyroJerkMag-std()"              
[41] "fBodyAcc-mean()-X"                    "fBodyAcc-mean()-Y"                   
[43] "fBodyAcc-mean()-Z"                    "fBodyAcc-std()-X"                    
[45] "fBodyAcc-std()-Y"                     "fBodyAcc-std()-Z"                    
[47] "fBodyAcc-meanFreq()-X"                "fBodyAcc-meanFreq()-Y"               
[49] "fBodyAcc-meanFreq()-Z"                "fBodyAccJerk-mean()-X"               
[51] "fBodyAccJerk-mean()-Y"                "fBodyAccJerk-mean()-Z"               
[53] "fBodyAccJerk-std()-X"                 "fBodyAccJerk-std()-Y"                
[55] "fBodyAccJerk-std()-Z"                 "fBodyAccJerk-meanFreq()-X"           
[57] "fBodyAccJerk-meanFreq()-Y"            "fBodyAccJerk-meanFreq()-Z"           
[59] "fBodyGyro-mean()-X"                   "fBodyGyro-mean()-Y"                  
[61] "fBodyGyro-mean()-Z"                   "fBodyGyro-std()-X"                   
[63] "fBodyGyro-std()-Y"                    "fBodyGyro-std()-Z"                   
[65] "fBodyGyro-meanFreq()-X"               "fBodyGyro-meanFreq()-Y"              
[67] "fBodyGyro-meanFreq()-Z"               "fBodyAccMag-mean()"                  
[69] "fBodyAccMag-std()"                    "fBodyAccMag-meanFreq()"              
[71] "fBodyBodyAccJerkMag-mean()"           "fBodyBodyAccJerkMag-std()"           
[73] "fBodyBodyAccJerkMag-meanFreq()"       "fBodyBodyGyroMag-mean()"             
[75] "fBodyBodyGyroMag-std()"               "fBodyBodyGyroMag-meanFreq()"         
[77] "fBodyBodyGyroJerkMag-mean()"          "fBodyBodyGyroJerkMag-std()"          
[79] "fBodyBodyGyroJerkMag-meanFreq()"      "angle(tBodyAccMean,gravity)"         
[81] "angle(tBodyAccJerkMean),gravityMean)" "angle(tBodyGyroMean,gravityMean)"    
[83] "angle(tBodyGyroJerkMean,gravityMean)" "angle(X,gravityMean)"                
[85] "angle(Y,gravityMean)"                 "angle(Z,gravityMean)" 


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
